Latex Tikz Examples, Discrete and Continuous Strategy Trees

### 2020-01-01 _other/tikz/tree/fs_tikz_gametree.tex
Updates from Overleaf

>>>>

\section{Grow Tree towards Different Directions}

\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]
\tikzstyle{level 1}=[level distance=10mm,sibling distance=10mm]
\tikzstyle{level 2}=[level distance=12mm,sibling distance=7mm]
\tikzstyle{level 3}=[level distance=6mm,sibling distance=6mm]
\tikzstyle{level 4}=[level distance=4mm,sibling distance=4mm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{} 
[grow=right]
child{
    [red]
    node(1)[solid node, label=below:{red dot}]{}
    }
child{
    [purple]
    node(2)[solid node]{}
    [grow=right]
    child
    child{
        [black]
        node(4)[hollow node, green]{}
        [grow=right]
        child
        child{
            [grow=right]
            child
            child
            child
            }
        }
    child
    child
    child{
            [black]
            node(5)[hollow node, red]{}
            [grow=up]
            child
            child
        }
    }
child{
    [black]
    node(3)[solid node, label=above:{hi there}, green]{}
    };
\end{tikzpicture}
\end{center}

\section{Continuous and Discrete}
